Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-05-28 Paper/Paper.tex
more modifs

% added by tbm
\usepackage{subfloat,subfig}
\setlength{\abovecaptionskip}{-3pt}
\setlength{\belowcaptionskip}{6pt}

@@

% Three addresses
% --------------
\threeauthors
  {Thierry Bertin-Mahieux} {Columbia University\\ {\tt tb2332@columbia.edu}}
  {Ron J. Weiss} {New York University \\ {\tt ronw@nyu.edu}}
  {Dan Ellis} {Columbia University \\ {\tt dpwe@ee.columbia.edu}}
% what order do we use? Thierry, Ron, Dan?  Dan, Thierry, Ron?

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.4\columnwidth]{code}
\end{center}
\caption{\small{A typical codeword from a codebook of size $200$ (code
    7 in Figure \ref{fig:codes1}), corresponding to a
    tonic-subdominant chord progression.  The patch is composed of $2$
    bars and the pattern length was set to $8$ beats.  }}
\label{fig:code}
\end{figure}

@@

\section{Applications}\label{sec:exps2}
We present two applications of the beat-chroma codebooks
to illustrate how the ``natural'' structure identified via 
unsupervised clustering can provide useful 
features for subsequent supervised tasks.  We will discuss how 
the codewords can be used in song segmentation, and for artist
recognition.  
%The representation created from large collections
%captures meaningful information without being forced to do so.
%
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

\subsection{Song Segmentation} \label{ssec:segment}

@@

\begin{table}
\begin{center}
\begin{tabular}{cc}
\toprule
Offset & \% of times chosen \\
\midrule
0 & $\mathbf{62.6}$\\
1 & $16.5$\\
2 & $\text{ }9.4$\\
3 & $11.5$\\
\bottomrule
\end{tabular}
\end{center}
\caption{\small{
Song segmentation experiment:
offsets relative to ground-truth 4-beat bar boundaries 
that gave minimum distortion encodings from the bar-aligned codebook.
%The real one is $0$.
%Random guess gives an accuracy of $25$\%.
}}
\label{tab:offset}
\end{table}

@@

\section{Conclusion and Future Work}
We have presented a practical method to perform large-scale clustering of
tonal patterns, and assessed the basic properties of the method through
experiments on a large collection of music. We have explored several ways
to inspect and interpret the data 
%(such as LLE) 
and suggested the merit of the representation
through further experiments.
We have discussed the possibility to move to even larger scales
and we provide our source code for other interested researchers.
\footnote{See \textit{Papers} section at \url{www.columbia.edu/~tb2332/}}

@@

%\small
\section{Acknowledgements}
Thanks to Graham Grindlay for numerous discussions and helpful comments.
T. Bertin-Mahieux is supported by a NSERC scholarship.
This material is based upon work supported by the IMLS (grant LG-06-08-0073-08).

>>>>

% added by tbm
\usepackage{subfloat,subfig}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{6pt}

@@

% Three addresses
% --------------
\threeauthors
  {Thierry Bertin-Mahieux} {Columbia University\\ {\tt tb2332@columbia.edu}}
  {Ron J. Weiss} {New York University \\ {\tt ronw@nyu.edu}}
  {Daniel P. W. Ellis} {Columbia University \\ {\tt dpwe@ee.columbia.edu}}
% what order do we use? Thierry, Ron, Dan?  Dan, Thierry, Ron?

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.4\columnwidth]{code_axis}
\end{center}
\caption{\small{A typical codeword from a codebook of size $200$ (code
    7 in Figure \ref{fig:codes1}), corresponding to a
    tonic-subdominant chord progression.  The patch is composed of $2$
    bars and the pattern length was set to $8$ beats.  }}
\label{fig:code}
\end{figure}

@@

\section{Applications}\label{sec:exps2}
We present two applications of the beat-chroma codebooks
to illustrate how the ``natural'' structure identified via 
unsupervised clustering can provide useful 
features for subsequent supervised tasks.  We will discuss how 
the codewords can be used in bar alignment, and for artist
recognition.  
%The representation created from large collections
%captures meaningful information without being forced to do so.
%
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

\subsection{Bar Alignment} \label{ssec:segment}

@@

\begin{table}
\begin{center}
\begin{tabular}{cc}
\toprule
Offset & \% of times chosen \\
\midrule
0 & $\mathbf{62.6}$\\
1 & $16.5$\\
2 & $\text{ }9.4$\\
3 & $11.5$\\
\bottomrule
\end{tabular}
\end{center}
\caption{\small{
Bar alignment experiment:
offsets relative to ground-truth 4-beat bar boundaries 
that gave minimum distortion encodings from the bar-aligned codebook.
%The real one is $0$.
%Random guess gives an accuracy of $25$\%.
}}
\label{tab:offset}
\end{table}

@@

\section{Conclusion and Future Work}
We have presented a practical method to perform large-scale clustering of
tonal patterns, and assessed the basic properties of the method through
experiments on a large collection of music. We have explored several ways
to inspect and interpret the data 
%(such as LLE) 
and suggested the merit of the representation
through further experiments.
We have discussed the possibility to move to even larger scales
and we provide our source code for other interested researchers
\footnote{See \textit{Papers} section at \url{www.columbia.edu/~tb2332/}}.

@@

%\small
\section{Acknowledgements}
Thanks to Graham Grindlay for numerous discussions and helpful comments.
T. Bertin-Mahieux is supported by a NSERC scholarship.
This material is based upon work supported by the IMLS (grant LG-06-08-0073-08)
and by NSF grant IIS-0713334. Any opinions, findings and
conclusions or recommendations expressed in this material are those of
the authors and do not necessarily reflect the views of the sponsors
